---
title: "ASSIGMENT__1"
author: "vivek rao kathheragandla"
date: "2024-01-26"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Importing the data.

#Source: chatGpt and github

#Downloaded the dataset and read it from my desktop.

```{r}
ship <- read.csv("C:\\Users\\KATHHERAGANDLA VIVEK\\Downloads\\titanic.csv")
#ship
#the above line would give the whole dataset.
```


***
#Descriptive analysis: This displays a summary of the whole dataset that we provided. The distribution, measures of variability (Standard Deviation, Range, Variance, Interquartile Range), and measures of central tendency (Mean, Median, Mode) are all included.
```{r}
#This function shows the first 6 rows and columns of the dataset
head(ship)
#This function shows the last 6 rows and columns of dataset.
tail(ship)
#This shows the whole summary that includes mean, median,mode and so on.
summary(ship)
```
***

#Transforming variables: There are several methods for doing this, including log, exponential, normalisation, and more.I decided to use Normalisation Transformation for this dataset.
#Normalization Transformation: This modifies the variable's scale such that the standard deviation increases to 1 and the mean to 0. Normalisation using the min-max or z-score methods might be used.I have the Titanic table with the Normalised Fare column.

```{r}
min_max <- function(x) {
  return((x - min(x)) / (max(x) - min(x)))}
#Here the Age got normalized and we can find that values in the Age_Norm column
ship$Age_norm <- min_max(ship$Age)
head(ship)
```

```{r}
#Log Transformation to Fare Column.
ship$Fare_log = log(ship$Fare)
ship$Fare_log
```

```{r}
hist(ship$Age, xlab = "Age", ylab = "Frequency",main = "Histogram_Age",col = "red")
#plot(ship$Age, xlab = "Age",ylab = "Frequency",main = "Histogram_Age)
```
***

#Marking the Scatter plot for Age and Fare
```{r}
#Age on the x-axis
x = ship$Age
#Fare on the y-axis
y = ship$Fare
plot(x,y, xlab ="Age",ylab = "Fare",main = "Age-Fare Plot",pch = 19,col =  "blue")

```

```{r}
x = ship$Age
y = ship$Pclass
plot(x,y, xlab ="Age",ylab = "Pclass",main = "Age-Pclass Plot",pch = 19,col =  "blue")
```

